WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-05-29 ms.tex
Add Fisher matrix elements

\marginpar{Actually, this does not give exactly the same Fisher matrix. Explain.}%
%
Another way is to plug the signal model from \Eref{eq:signal-model} \emph{evaluated at the ML parameter estimates} into the single-detector likelihood in \Eref{eq:gaussian-likelihood-spa}:
%
\begin{eqnarray*}
	\fl p\left(\hat{\boldsymbol\theta}_i \middle| \boldsymbol\theta \right)
	&:=&
	p\left(x_i(\omega) = h_i(\omega; \hat{\boldsymbol\theta}_i)
		\middle| \boldsymbol\theta \right)
	\\\fl
	&\propto& \exp \left[
		- \frac{1}{2} \int_0^\infty \frac{\left|
			\frac{\hat{\rho}_i}{\sigma_i(\hat{\boldsymbol\theta}_\mathrm{in})} e^{i (\hat\gamma_i - \omega \hat\tau_i)} h(\omega; \hat{\boldsymbol\theta}_\mathrm{in})
			- \frac{\rho_i}{\sigma_i(\boldsymbol\theta_\mathrm{in})} e^{i (\gamma_i - \omega \tau_i)} h(\omega; \boldsymbol\theta_\mathrm{in})
		\right|^2}{S_i(\omega)} \, d\omega
	\right].
\end{eqnarray*}
%
If we assume that $\hat{\boldsymbol\theta}_\mathrm{in} = \boldsymbol\theta_\mathrm{in}$, then this reduces to
%
\begin{equation}
	p\left(\hat\rho_i, \hat\gamma_i, \hat\tau_i
		\middle| \rho_i, \gamma_i, \tau_i \right) \propto
	\exp \left[ - \frac{1}{2}{\hat\rho_i}^2 - \frac{1}{2}{\rho_i}^2
		+ \hat\rho_i \rho_i \Re \left\{ e^{i \tilde{\gamma}_i} a_i^*(\tilde{\tau}_i)
		\right\}
	\right]
\end{equation}
%
with $\tilde{\gamma}_i = \hat\gamma_i - \gamma_i$, $\tilde{\tau}_i = \hat\tau_i - \tau_i$, and the template's autocorrelation function $a_i(t; \boldsymbol\theta_\mathrm{in})$ defined as
%
\begin{equation}
	a_i(t; \boldsymbol\theta_\mathrm{in}) := \frac{1}{{{\sigma_i}^2(\boldsymbol\theta_\mathrm{in})}} \int_0^\infty \frac{\left| h(\omega; \hat{\boldsymbol\theta}_\mathrm{in})\right|^2}{S_i(\omega)} e^{i \omega t} \,d\omega.
\end{equation}

@@

>>>>

\marginpar{Actually, this does not give exactly the same Fisher matrix. Explain.}%
%
Another way is to plug the signal model from \Eref{eq:signal-model} \emph{evaluated at the ML parameter estimates} into the single-detector likelihood in \Eref{eq:gaussian-likelihood-spa}:
%
\begin{eqnarray*}
	\fl p\left(\hat{\boldsymbol\theta}_i \middle| \boldsymbol\theta \right)
	&:=&
	p\left(x_i(\omega) = h_i(\omega; \hat{\boldsymbol\theta}_i)
		\middle| \boldsymbol\theta \right)
	\\\fl
	&\propto& \exp \left[
		- \frac{1}{2} \int_0^\infty \frac{\left|
			\frac{\hat{\rho}_i}{\sigma_i(\hat{\boldsymbol\theta}_\mathrm{in})} e^{i (\hat\gamma_i - \omega \hat\tau_i)} h(\omega; \hat{\boldsymbol\theta}_\mathrm{in})
			- \frac{\rho_i}{\sigma_i(\boldsymbol\theta_\mathrm{in})} e^{i (\gamma_i - \omega \tau_i)} h(\omega; \boldsymbol\theta_\mathrm{in})
		\right|^2}{S_i(\omega)} \, d\omega
	\right].
\end{eqnarray*}
%
If we assume that $\hat{\boldsymbol\theta}_\mathrm{in} = \boldsymbol\theta_\mathrm{in}$, then this reduces to
%
\begin{equation}\label{eq:autocor-likelihood}
	p\left(\hat\rho_i, \hat\gamma_i, \hat\tau_i
		\middle| \rho_i, \gamma_i, \tau_i \right) \propto
	\exp \left[ - \frac{1}{2}{\hat\rho_i}^2 - \frac{1}{2}{\rho_i}^2
		+ \hat\rho_i \rho_i \Re \left\{ e^{i \tilde{\gamma}_i} a_i^*(\tilde{\tau}_i)
		\right\}
	\right]
\end{equation}
%
with $\tilde{\gamma}_i = \hat\gamma_i - \gamma_i$, $\tilde{\tau}_i = \hat\tau_i - \tau_i$, and the template's autocorrelation function $a_i(t; \boldsymbol\theta_\mathrm{in})$ defined as
%
\begin{equation}
	a_i(t; \boldsymbol\theta_\mathrm{in}) := \frac{1}{{{\sigma_i}^2(\boldsymbol\theta_\mathrm{in})}} \int_0^\infty \frac{\left| h(\omega; \hat{\boldsymbol\theta}_\mathrm{in})\right|^2}{S_i(\omega)} e^{i \omega t} \,d\omega.
\end{equation}

@@

\subsection{Properties}

Fisher matrix elements of \Eref{eq:autocor-likelihood}, with detector subscript suppressed:
%
\begin{eqnarray}
	\nonumber
	\mathcal{I}_{\rho\rho} &=& 1 \\
	\nonumber
	\mathcal{I}_{\rho\gamma} &=& 0 \\
	\nonumber
	\mathcal{I}_{\rho\tau} &=& 0 \\
	\mathcal{I}_{\gamma\gamma} &=& \frac{\rho^2}{2}
		\int_{-\infty}^\infty \left|a(t)\right|^2 w(t; \rho) dt \\
	\mathcal{I}_{\tau\tau} &=& -\frac{\rho^2}{2}
		\int_{-\infty}^\infty \Re\left[a^*(t) a''(t)\right] w(t; \rho) dt \\
	\mathcal{I}_{\gamma\tau} &=& -\frac{\rho^2}{2}
		\int_{-\infty}^\infty \Im\left[a^*(t) a'(t)\right] w(t; \rho) dt \\
	\nonumber\textrm{where} && \\
	\nonumber
	a'(t) &=& \frac{\partial a}{\partial t} \\
	\nonumber
	a''(t) &=& \frac{\partial^2 a}{\partial t^2} \\
	\nonumber
	w(t; \rho) &=& \frac{
		\displaystyle
		\exp\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\left(
		I_0\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right] +
		I_1\left[\frac{\rho^2}{4}\left|a(t)\right|^2\right]
		\right)
	}{
		\displaystyle
		\int_{-\infty}^\infty
		\exp\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		I_0\left[\frac{\rho^2}{4}\left|a(t')\right|^2\right]
		dt'
	}.
\end{eqnarray}

If we can show that the common factor approaches a delta function, $w(t; \rho) \rightarrow \delta(t)$ as $\rho \rightarrow \infty$, then the Fisher matrix approaches \Eref{eq:fisher-matrix} as $\rho \rightarrow \infty$.
